---
title: "analysis"
author: "Iris Zhong"
date: "4/27/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nlme)
library(tidyverse)
library(report)
library(stargazer)
library(papaja)
```

```{r}
library(readr)
data_pair <- read_csv("data_pair.csv")
data_pair$day_of_study_A <- as.numeric(data_pair$day_of_study_A)
data_pair$day_of_study_P <- as.numeric(data_pair$day_of_study_P)
data_pair <- data_pair %>%
  mutate(day_of_study_A = day_of_study_A -1,
         day_of_study_P = day_of_study_P - 1,
         fair_chores_C_A = fair_chores_A - mean(fair_chores_A, na.rm = T),
         fair_chores_C_P = fair_chores_P - mean(fair_chores_P, na.rm = T),
         grbs_C_A = grbs_ss_A - mean(grbs_ss_A, na.rm = T),
         grbs_C_P = grbs_ss_P - mean(grbs_ss_P, na.rm = T))
```


```{r}
plot1 <- ggplot(data_pair, aes(x = fair_chores_C_A, y = qmi_ss_A, color = factor(gender_chr_A, labels = c("Men","Women")), shape= factor(gender_chr_A, labels = c("Men","Women")))) +
  geom_point()+
  geom_jitter() +
  geom_smooth(method = "lm", aes(linetype = factor(gender_chr_A, labels = c("Men","Women"))), se=F) +
  scale_color_grey(start = 0.3, end = 0.5) +
  theme_bw() +
  scale_y_continuous(limits = c(1, 4), oob = scales::squish) +
  labs(x = "Perceived chore fairness score (Centered)", y = "QMI score", color = "Gender", shape = "Gender", linetype = "Gender") +
 scale_fill_manual(labels = c("Men", "Women"))

# ggsave("qmi_fairness.png")
```


```{r, include = F}
ggplot(data_pair, aes(x = fair_chores_A)) +
  geom_histogram()
```



# Satisfaction ~ chore

```{r}
ggplot(data_pair, aes(x = as.factor(fair_chores_A), y = qmi_ss_A )) +
  geom_boxplot() +
  facet_wrap(~gender_chr_A) 
```

```{r}
ggplot(data_pair, aes(x = as.factor(day_of_study_A), y = qmi_ss_A)) +
  geom_boxplot()+
  facet_wrap(~gender_chr_A) +
  geom_jitter(alpha = 0.2)
```

```{r}

```


## 1. qmi ~ gender + fair_chores_A * gender (+ telework * gender + day_of_study * gender)

```{r qmi chore 1}
fairness_grbs  <- lme(fair_chores_C_A ~ gender_chr_A + 
                          telework_A:gender_chr_A +
                          gender_chr_A:day_of_study_A + 
                          grbs_C_A:gender_chr_A -1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(fairness_grbs)

```


```{r qmi chore 1}
mod_qmi_chore_1  <- lme(qmi_ss_A ~ gender_chr_A + 
                          telework_A:gender_chr_A +
                          gender_chr_A:day_of_study_A + 
                          fair_chores_C_A:gender_chr_A -1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_1)

```

```{r qmi chore 1 mod}
mod_qmi_chore_1_mod  <- lme(qmi_ss_A ~ genderE_A + 
                          telework_A:genderE_A +
                          genderE_A:day_of_study_A + 
                          fair_chores_C_A:genderE_A,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_1_mod)

```

## 2. qmi ~ gender + fair_chores_A * gender + fair_chores_P * gender (+ telework * gender + day_of_study * gender) 

```{r qmi chore 2}
mod_qmi_chore_2  <- lme(qmi_ss_A ~ gender_chr_A + 
                          telework_A:gender_chr_A +
                             gender_chr_A:day_of_study_A + 
                             fair_chores_C_A:gender_chr_A +
                             fair_chores_C_P:gender_chr_A -1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_2)

```

```{r qmi chore 2 mod}
mod_qmi_chore_2_mod  <- lme(qmi_ss_A ~ genderE_A + 
                          telework_A:genderE_A +
                             genderE_A:day_of_study_A + 
                             fair_chores_C_A:genderE_A +
                             fair_chores_C_P:genderE_A,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_2_mod)

```


## 3. qmi ~ gender + fair_chores_A * gender + fair_chores_P * gender + grbs * gender + grbs * fair_chores_A * gender + grbs * fair_chores_P * gender (+ telework * gender + day_of_study * gender) 

```{r qmi chore 3}
mod_qmi_chore_3  <- lme(qmi_ss_A ~ gender_chr_A + 
                          telework_A:gender_chr_A +
                               gender_chr_A:day_of_study_A +
                               fair_chores_C_A:gender_chr_A +
                               fair_chores_C_P:gender_chr_A + 
                               gender_chr_A:grbs_C_A+             
                               grbs_C_A:gender_chr_A:fair_chores_C_A+
                               grbs_C_A:gender_chr_A:fair_chores_C_P -1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_3)
#report(mod_qmi_chore_3)
```


```{r qmi chore 3 mod}
mod_qmi_chore_3_mod  <- lme(qmi_ss_A ~ genderE_A + 
                          telework_A:genderE_A +
                               genderE_A:day_of_study_A +
                               fair_chores_C_A:genderE_A +
                               fair_chores_C_P:genderE_A + 
                               genderE_A:grbs_C_A+             
                               grbs_C_A:genderE_A:fair_chores_C_A+
                               grbs_C_A:genderE_A:fair_chores_C_P,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_3_mod)
#report(mod_qmi_chore_3)
```


## R^2

```{r qmi chore empty}
mod_qmi_chore_empty<- lme(qmi_ss_A ~ gender_chr_A - 1,
                     data = data_pair,
                     random = ~ gender_chr_A - 1|dyadID,
                     correlation = corCompSymm(form = ~1|dyadID/obsid), 
                     weights = varIdent(form = ~1|gender_chr_A), 
                     na.action = na.omit)

summary(mod_qmi_chore_empty)
```


residual standard deviation for women: 0.4064918
residual standard deviation for men: 0.4064918 * 0.8740537 
residual variance: square them


Calculate pseudo-R^2:

```{r qmi chore R2}
resid_var_qmi_chore_W <- 0.4064918^2
resid_var_qmi_chore_M <- (0.4064918 * 0.8740537)^2
r2_qmi_chore_W1 <- 1 - (0.4051607^2)/resid_var_qmi_chore_W
r2_qmi_chore_M1 <- 1 - (0.4051607*0.8741175)^2/resid_var_qmi_chore_M
r2_qmi_chore_W2 <- 1 - (0.4052860^2)/resid_var_qmi_chore_W
r2_qmi_chore_M2 <- 1 - (0.4052860*0.8741499)^2/resid_var_qmi_chore_M
r2_qmi_chore_W3 <- 1 - (0.4055747^2)/resid_var_qmi_chore_W
r2_qmi_chore_M3 <- 1 - (0.4055747*0.8739182)^2/resid_var_qmi_chore_M
```

# Chore ~ Telework

```{r}
ggplot(data_pair, aes(x = as.factor(telework_A), y = fair_chores_C_A)) +
  geom_boxplot() +
  facet_wrap(~genderE_A)
```


## 1. (not used) Chore ~ gender + telework * gender (+ day_of_study * gender)
```{r, include = F}
mod_chore_work  <- lme(fair_chores_C_A ~ gender_chr_A + day_of_study_A:gender_chr_A+ telework_A:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work)
```

## 2. Chore ~ gender + telework * gender (+ day_of_study * gender + childnum + r_years + income)

```{r chore work}
mod_chore_work_2  <- lme(fair_chores_C_A ~ gender_chr_A +
                           day_of_study_A:gender_chr_A + 
                           telework_A:gender_chr_A + 
                           childnum + r_years + income_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work_2)
#report(mod_chore_work_2)
```

## Mod 2 Moderation

```{r chore work mod}
mod_chore_work_2_mod  <- lme(fair_chores_C_A ~ genderE_A + 
                               telework_A:genderE_A + childnum + r_years + income_A,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work_2_mod)

```

## R^2

```{r chore work empty}
mod_chore_work_empty<- lme(fair_chores_C_A ~ gender_chr_A - 1,
                     data = data_pair,
                     random = ~ gender_chr_A - 1|dyadID,
                     correlation = corCompSymm(form = ~1|dyadID/obsid), 
                     weights = varIdent(form = ~1|gender_chr_A), 
                     na.action = na.omit)

summary(mod_chore_work_empty)
```

```{r chore work R2}
resid_var_chore_work_W <- 0.6076890^2
resid_var_chore_work_M <- (0.6076890 * 0.9637828)^2
r2_chore_work_W <- 1 - (0.6042395^2)/resid_var_chore_work_W
r2_chore_work_M <- 1 - (0.6042395*0.9601972)^2/resid_var_chore_work_M

```

# Satisfaction ~ Telework

## qmi ~ gender + telework * gender (+ day_of_study * gender)

```{r qmi work}
mod_work_qmi  <- lme(qmi_ss_A ~ gender_chr_A + 
                       day_of_study_A:gender_chr_A +
                       telework_A:gender_chr_A-1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_work_qmi)

```

```{r qmi work mod}
mod_work_qmi_mod  <- lme(qmi_ss_A ~ genderE_A + 
                       day_of_study_A:genderE_A +
                       telework_A:genderE_A,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_work_qmi_mod)

```

```{r}
ggplot(data_pair, aes(x = as.factor(telework_A), y = qmi_ss_A)) +
  geom_boxplot()
```



## R^2


```{r qmi work empty}
mod_qmi_work_empty<- lme(qmi_ss_A ~ gender_chr_A - 1,
                     data = data_pair,
                     random = ~ gender_chr_A - 1|dyadID,
                     correlation = corCompSymm(form = ~1|dyadID/obsid), 
                     weights = varIdent(form = ~1|gender_chr_A), 
                     na.action = na.omit)

summary(mod_qmi_work_empty)
```


```{r qmi work R2}
resid_var_qmi_work_W <- 0.4064918^2
resid_var_qmi_work_M <- (0.4064918 * 0.8740537)^2
r2_qmi_work_W <- 1 - (0.4061178^2)/resid_var_qmi_work_W
r2_qmi_work_M<- 1 - ((0.4061178*0.8749703)^2)/resid_var_qmi_work_M
r2_qmi_work_W
r2_qmi_work_M
resid_var_qmi_work_M
(0.4061178*0.8749703)^2

```

```{r, results = "asis"}
stargazer(mod_qmi_chore_1, mod_qmi_chore_2, mod_qmi_chore_3, type = "html",
          title = "Relationship between satisfaction, perceived chore fairness and gender ideology",
          dep.var.labels=c("Relationship satisfaction"),
          covariate.labels=c("Men","Women", "Men * Telework", "Women * Telework", "Men * Day of study", "Women * Day of study", "Men * Actor chore fairness", "Women * Actor chore fairness", "Men * Partner chore fairness","Women * Partner chore fairness","Man * Gender ideology", "Woman * Gender ideology", "Man * Actor chore fairness * Gender ideology","Woman * Actor chore fairness * Gender ideology","Man * Partner chore fairness * Gender ideology","Woman * Partner chore fairness * Gender ideology" ))
```

```{r, results = "asis"}
stargazer(mod_work_qmi, type = "html",
          title = "Relationship between telework and relationship satisfaction",
          dep.var.labels=c("Relationship satisfaction"),
          covariate.labels=c("Men","Women", "Men * Day of study", "Women * Day of study","Men * Telework", "Women * Telework" ))
```

```{r, results = "asis"}
stargazer(mod_chore_work_2, type = "html",
          title = "Relationship between perceived chore fairness and telework",
          dep.var.labels=c("Perceived chore fairness"),
          covariate.labels=c("Men","Women", "Number of children", "Relationship length", "Income", "Men * Day of study","Women * Day of study","Men * Telework","Women * Telework" ))
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{3}{c}{qmi\_ss\_A} \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 gender\_chr\_AM & 3.606$^{***}$ & 3.606$^{***}$ & 3.590$^{***}$ \\ 
  & (0.087) & (0.087) & (0.090) \\ 
  & & & \\ 
 gender\_chr\_AW & 3.387$^{***}$ & 3.387$^{***}$ & 3.386$^{***}$ \\ 
  & (0.096) & (0.096) & (0.097) \\ 
  & & & \\ 
 gender\_chr\_AM:telework\_A & $-$0.078 & $-$0.078 & $-$0.067 \\ 
  & (0.094) & (0.094) & (0.096) \\ 
  & & & \\ 
 gender\_chr\_AW:telework\_A & 0.054 & 0.054 & 0.062 \\ 
  & (0.096) & (0.096) & (0.096) \\ 
  & & & \\ 
 gender\_chr\_AM:day\_of\_study\_A & $-$0.003 & $-$0.003 & $-$0.003 \\ 
  & (0.003) & (0.003) & (0.003) \\ 
  & & & \\ 
 gender\_chr\_AW:day\_of\_study\_A & 0.007$^{**}$ & 0.007$^{**}$ & 0.006$^{*}$ \\ 
  & (0.003) & (0.003) & (0.003) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A & 0.069$^{***}$ & 0.069$^{***}$ & 0.072$^{***}$ \\ 
  & (0.018) & (0.019) & (0.019) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A & 0.085$^{***}$ & 0.082$^{***}$ & 0.076$^{***}$ \\ 
  & (0.019) & (0.020) & (0.021) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_P &  & $-$0.008 & $-$0.007 \\ 
  &  & (0.018) & (0.018) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_P &  & $-$0.003 & $-$0.003 \\ 
 & (0.003) & (0.003) & (0.003) \\ 
  & & & \\ 
 gender\_chr\_AW:day\_of\_study\_A & 0.007$^{**}$ & 0.007$^{**}$ & 0.006$^{*}$ \\ 
  & (0.003) & (0.003) & (0.003) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A & 0.069$^{***}$ & 0.069$^{***}$ & 0.072$^{***}$ \\ 
  & (0.018) & (0.019) & (0.019) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A & 0.085$^{***}$ & 0.082$^{***}$ & 0.076$^{***}$ \\ 
  & (0.019) & (0.020) & (0.021) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_P &  & $-$0.008 & $-$0.007 \\ 
  &  & (0.018) & (0.018) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_P &  & $-$0.003 & $-$0.003 \\ 
  &  & (0.021) & (0.022) \\ 
  & & & \\ 
 gender\_chr\_AM:grbs\_C\_A &  &  & 0.060 \\ 
 &  &  & (0.084) \\ 
  & & & \\ 
 gender\_chr\_AW:grbs\_C\_A &  &  & 0.035 \\ 
  &  &  & (0.075) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A:grbs\_C\_A &  &  & $-$0.035 \\ 
  &  &  & (0.025) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A:grbs\_C\_A &  &  & $-$0.038 \\ 
  &  &  & (0.030) \\ 
  & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_P:grbs\_C\_A &  &  & 0.002 \\ 
  &  &  & (0.029) \\ 
  & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_P:grbs\_C\_A &  &  & $-$0.016 \\ 
  &  &  & (0.029) \\ 
   & & & \\ 
\hline \\[-1.8ex] 
Observations & 2,107 & 2,107 & 2,107 \\ 
Log Likelihood & $-$1,160.550 & $-$1,166.468 & $-$1,178.435 \\ 
Akaike Inf. Crit. & 2,349.100 & 2,364.937 & 2,400.871 \\ 
Bayesian Inf. Crit. & 2,428.189 & 2,455.309 & 2,525.070 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

