---
title: "analysis"
author: "Iris Zhong"
date: "4/27/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nlme)
library(tidyverse)
library(report)
library(stargazer)
```

```{r}
library(readr)
data_pair <- read_csv("data_pair.csv")
data_pair$day_of_study_A <- as.numeric(data_pair$day_of_study_A)
data_pair$day_of_study_P <- as.numeric(data_pair$day_of_study_P)
data_pair <- data_pair %>%
  mutate(day_of_study_A = day_of_study_A -1,
         day_of_study_P = day_of_study_P - 1,
         fair_chores_C_A = fair_chores_A - mean(fair_chores_A, na.rm = T),
         fair_chores_C_P = fair_chores_P - mean(fair_chores_P, na.rm = T),
         grbs_C_A = grbs_ss_A - mean(grbs_ss_A, na.rm = T),
         grbs_C_P = grbs_ss_P - mean(grbs_ss_P, na.rm = T))
```

```{r}
ggplot(data_pair, aes(x = fair_chores_A, y = qmi_ss_A)) +
  geom_point()+
  geom_jitter() +
  geom_smooth(method = "lm")
```



```{r}
mod_qmi_chore  <- lme(qmi_ss_A ~ gender_chr_A + gender_chr_A:day_of_study_A + fair_chores_C_A:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore)
stargazer(mod_qmi_chore)
```


\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & qmi\_ss\_A \\ 
\hline \\[-1.8ex] 
 gender\_chr\_AM & 3.563$^{***}$ \\ 
  & (0.070) \\ 
  & \\ 
 gender\_chr\_AW & 3.426$^{***}$ \\ 
  & (0.066) \\ 
  & \\ 
 gender\_chr\_AM:day\_of\_study\_A & $-$0.003 \\ 
  & (0.003) \\ 
  & \\ 
 gender\_chr\_AW:day\_of\_study\_A & 0.007$^{**}$ \\ 
  & (0.003) \\ 
  & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A & 0.069$^{***}$ \\ 
  & (0.018) \\ 
  & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A & 0.085$^{***}$ \\ 
  & (0.019) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,107 \\ 
Log Likelihood & $-$1,157.993 \\ 
Akaike Inf. Crit. & 2,339.985 \\ 
Bayesian Inf. Crit. & 2,407.787 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

```{r}
mod_qmi_chore_APIM  <- lme(qmi_ss_A ~ gender_chr_A + gender_chr_A:day_of_study_A + fair_chores_C_A:gender_chr_A+fair_chores_C_P:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_APIM)
```


```{r}
mod_qmi_chore_APIM_2  <- lme(qmi_ss_A ~ gender_chr_A + gender_chr_A:day_of_study_A + fair_chores_C_A:gender_chr_A+fair_chores_C_P:gender_chr_A + gender_chr_A:grbs_C_A+ grbs_C_A:gender_chr_A:fair_chores_C_A+grbs_C_A:gender_chr_A:fair_chores_C_P+  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_APIM_2)
report(mod_qmi_chore_APIM_2)
```
grbs_ss_A:fair_chores_C_A + grbs_ss_A:fair_chores_C_P

```{r}
mod_chore_work  <- lme(fair_chores_C_A ~ gender_chr_A + telework_A:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work)
```

```{r}
mod_chore_work_2  <- lme(fair_chores_C_A ~ genderE_A + telework_A:genderE_A + childnum + r_years + income_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work_2)
```

```{r}
mod_work_qmi  <- lme(qmi_ss_A ~ gender_chr_A + telework_A,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_work_qmi)
```