---
title: "analysis"
author: "Iris Zhong"
date: "4/27/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nlme)
library(tidyverse)
library(report)
library(stargazer)
```

```{r}
library(readr)
data_pair <- read_csv("data_pair.csv")
data_pair$day_of_study_A <- as.numeric(data_pair$day_of_study_A)
data_pair$day_of_study_P <- as.numeric(data_pair$day_of_study_P)
data_pair <- data_pair %>%
  mutate(day_of_study_A = day_of_study_A -1,
         day_of_study_P = day_of_study_P - 1,
         fair_chores_C_A = fair_chores_A - mean(fair_chores_A, na.rm = T),
         fair_chores_C_P = fair_chores_P - mean(fair_chores_P, na.rm = T),
         grbs_C_A = grbs_ss_A - mean(grbs_ss_A, na.rm = T),
         grbs_C_P = grbs_ss_P - mean(grbs_ss_P, na.rm = T))
```

```{r}
ggplot(data_pair, aes(x = fair_chores_A, y = qmi_ss_A, color= gender_chr_A, shape= gender_chr_A)) +
  geom_point()+
  geom_jitter() +
  geom_smooth(method = "lm")
```


```{r}
ggplot(data_pair, aes(x = fair_chores_A)) +
  geom_histogram()
```




```{r}
mod_qmi_chore  <- lme(qmi_ss_A ~ gender_chr_A + gender_chr_A:day_of_study_A + fair_chores_C_A:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore)
#stargazer(mod_qmi_chore)
```


```{r}
mod_qmi_chore_APIM  <- lme(qmi_ss_A ~ gender_chr_A + 
                             gender_chr_A:day_of_study_A + 
                             fair_chores_C_A:gender_chr_A +
                             fair_chores_C_P:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_APIM)
#stargazer(mod_qmi_chore,mod_qmi_chore_APIM)
```


\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{qmi\_ss\_A} \\ 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 gender\_chr\_AM & 3.563$^{***}$ & 3.563$^{***}$ \\ 
  & (0.070) & (0.070) \\ 
  & & \\ 
 gender\_chr\_AW & 3.426$^{***}$ & 3.426$^{***}$ \\ 
  & (0.066) & (0.067) \\ 
  & & \\ 
 gender\_chr\_AM:day\_of\_study\_A & $-$0.003 & $-$0.003 \\ 
  & (0.003) & (0.003) \\ 
  & & \\ 
 gender\_chr\_AW:day\_of\_study\_A & 0.007$^{**}$ & 0.007$^{**}$ \\ 
  & (0.003) & (0.003) \\ 
  & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A & 0.069$^{***}$ & 0.069$^{***}$ \\ 
  & (0.018) & (0.019) \\ 
  & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A & 0.085$^{***}$ & 0.082$^{***}$ \\ 
  & (0.019) & (0.020) \\ 
  & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_P &  & $-$0.008 \\ 
  &  & (0.018) \\ 
  & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_P &  & $-$0.003 \\ 
  &  & (0.021) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 2,107 & 2,107 \\ 
Log Likelihood & $-$1,157.993 & $-$1,163.909 \\ 
Akaike Inf. Crit. & 2,339.985 & 2,355.818 \\ 
Bayesian Inf. Crit. & 2,407.787 & 2,434.907 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

```{r}
mod_qmi_chore_APIM_2  <- lme(qmi_ss_A ~ gender_chr_A + 
                               gender_chr_A:day_of_study_A +
                               fair_chores_C_A:gender_chr_A +
                               fair_chores_C_P:gender_chr_A + 
                               gender_chr_A:grbs_C_A+             
                               grbs_C_A:gender_chr_A:fair_chores_C_A+
                               grbs_C_A:gender_chr_A:fair_chores_C_P+  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_qmi_chore_APIM_2)
report(mod_qmi_chore_APIM_2)
```

```{r}
mod_qmi_chore_empty<- lme(qmi_ss_A ~ gender_chr_A - 1,
                     data = data_pair,
                     random = ~ gender_chr_A - 1|dyadID,
                     correlation = corCompSymm(form = ~1|dyadID/obsid), 
                     weights = varIdent(form = ~1|gender_chr_A), 
                     na.action = na.omit)

summary(mod_qmi_chore_empty)
```


residual standard deviation for women: 0.4064918
residual standard deviation for men: 0.4064918 * 0.8740537 
residual variance: square them


```{r}
mod_chore_work  <- lme(fair_chores_C_A ~ gender_chr_A + telework_A:gender_chr_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work)
```

```{r}
mod_chore_work_2  <- lme(fair_chores_C_A ~ gender_chr_A + telework_A:gender_chr_A + childnum + r_years + income_A  - 1,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_chore_work_2)
report(mod_chore_work_2)
```





```{r}
mod_work_qmi  <- lme(qmi_ss_A ~ gender_chr_A + telework_A + telework_P,
                      data = data_pair, 
                      random = ~ gender_chr_A - 1|dyadID,
                      correlation = corCompSymm(form = ~1|dyadID/obsid),
                      weights = varIdent(form = ~1|gender_chr_A),
                      na.action = na.omit)

summary(mod_work_qmi)
#stargazer(mod_work_qmi, mod_chore_work_2, mod_qmi_chore,mod_qmi_chore_APIM)
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & qmi\_ss\_A & fair\_chores\_C\_A & \multicolumn{2}{c}{qmi\_ss\_A} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 gender\_chr\_AM &  &  & 3.563$^{***}$ & 3.563$^{***}$ \\ 
  &  &  & (0.070) & (0.070) \\ 
  & & & & \\ 
 gender\_chr\_AW & $-$0.084$^{*}$ &  & 3.426$^{***}$ & 3.426$^{***}$ \\ 
  & (0.049) &  & (0.066) & (0.067) \\ 
  & & & & \\ 
 telework\_A & $-$0.020 &  &  &  \\ 
  & (0.057) &  &  &  \\ 
  & & & & \\ 
 genderE\_A &  & $-$0.053 &  &  \\ 
  &  & (0.126) &  &  \\ 
  & & & & \\ 
 childnum &  & 0.048 &  &  \\ 
  &  & (0.073) &  &  \\ 
  & & & & \\ 
 r\_years &  & $-$0.006 &  &  \\ 
  &  & (0.005) &  &  \\ 
  & & & & \\ 
 income\_A &  & 0.00000 &  &  \\ 
  &  & (0.00000) &  &  \\ 
  & & & & \\ 
 genderE\_A:telework\_A &  & $-$0.028 &  &  \\ 
  &  & (0.158) &  &  \\ 
  & & & & \\ 
 gender\_chr\_AM:day\_of\_study\_A &  &  & $-$0.003 & $-$0.003 \\ 
  &  &  & (0.003) & (0.003) \\ 
  & & & & \\ 
 gender\_chr\_AW:day\_of\_study\_A &  &  & 0.007$^{**}$ & 0.007$^{**}$ \\ 
  &  &  & (0.003) & (0.003) \\ 
  & & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_A &  &  & 0.069$^{***}$ & 0.069$^{***}$ \\ 
  &  &  & (0.018) & (0.019) \\ 
  & & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_A &  &  & 0.085$^{***}$ & 0.082$^{***}$ \\ 
  &  &  & (0.019) & (0.020) \\ 
  & & & & \\ 
 gender\_chr\_AM:fair\_chores\_C\_P &  &  &  & $-$0.008 \\ 
  &  &  &  & (0.018) \\ 
  & & & & \\ 
 gender\_chr\_AW:fair\_chores\_C\_P &  &  &  & $-$0.003 \\ 
  &  &  &  & (0.021) \\ 
  & & & & \\ 
 Constant & 3.560$^{***}$ &  &  &  \\ 
  & (0.077) &  &  &  \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 2,107 & 1,807 & 2,107 & 2,107 \\ 
Log Likelihood & $-$1,162.963 & $-$1,847.812 & $-$1,157.993 & $-$1,163.909 \\ 
Akaike Inf. Crit. & 2,343.926 & 3,717.624 & 2,339.985 & 2,355.818 \\ 
Bayesian Inf. Crit. & 2,394.790 & 3,778.087 & 2,407.787 & 2,434.907 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 