---
title: "Descriptive stats"
author: "Iris Zhong"
date: "3/31/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries}
library(tidyverse)
library(tidyr)
library(mosaic)
library(ggplot2)
library(here)
library(stargazer)
library(psychTools)
library(furniture)
```

```{r import data}
# import premeasures
prem <- read.csv("TeleCom_Dyad_premeasures.csv",fileEncoding = 'UTF-8-BOM')
# import daily diary
diary <- read.csv(here("TeleCom_Dyad_dailydiary.csv"))
```

```{r clean partID, include = F}
diary <- diary %>%
  mutate(partID = case_when(partID_given == "" ~ partID,
                            partID_given != "" ~ partID_given))
diary <- diary %>%
  mutate(partID = str_replace_all(partID, " ", ""),
         partID = str_replace_all(partID, ":", ""),
         partID = str_replace(partID, "R-", "R_"),
         partID = str_remove(partID,"\\."),
         partID = ifelse(str_starts(partID,"R", negate = T ),
                         paste0("R_",partID), partID))
         
```


```{r create relationship length}
prem$r_length <- as.Date(as.character(prem$RecordedDate), format="%m/%d/%y")-
                  as.Date(as.character(prem$relation_length), format="%m/%d/%y")

prem$r_years <- as.numeric(prem$r_length) 
prem <- prem %>%
  mutate(r_years = r_years/365)
```


```{r select var in prem}
prem_select <- prem %>%
  dplyr::select(partID = ResponseId, dyadID, gender, telework = Q139, age = birthday, r_years, race, childnum = people_5_TEXT, income = indinc)
```

```{r clean variables}
prem_select <- prem_select %>%
  mutate(telework = case_when(
    telework == "Yes, I am teleworking but my partner is not" ~ 1,
    telework == "Yes, my partner is teleworking but I am not" ~ 0,
    telework == "We are both teleworking" ~ 1),
    childnum = ifelse(is.na(childnum) == T, 0, childnum),
    gender = case_when(gender == "Woman" ~ 1,
                       gender == "Woman,Cis gendered" ~ 1,
                       gender == "Man" ~ 0,
                       gender == "Man,Cis gendered" ~ 0))
```

```{r factorize variables}
prem_select <- prem_select %>%
  mutate(telework = as.factor(telework),
         gender = as.factor(gender))
```



```{r, results = 'asis'}
stargazer(prem_select, type = "latex")
```


```{r, results = "asis"}
table1(prem_select, gender, age, r_years, race, childnum, income, splitby = ~telework, format_number = T, output = "markdown")
  
```



\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
dyadID & 364 & 26,018,185.000 & 9,455,389.000 & 377,033 & 28,947,773 & 31,423,023 & 33,735,733 \\ 
age & 364 & 45.802 & 8.350 & 26 & 39 & 52 & 74 \\ 
r\_years & 360 & 18.448 & 10.192 & $-$48.074 & 11.813 & 23.205 & 43.186 \\ 
childnum & 364 & 0.830 & 1.346 & 0 & 0 & 1 & 12 \\ 
income & 296 & 76,618.800 & 105,704.100 & 0.000 & 37,500.000 & 92,000.000 & 1,490,000.000 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table} 
Show in New WindowClear OutputExpand/Collapse Output
\begin{table}[ ht ] 
\centering 
\caption{}\label{}
\begin{tabular}{ l c c }
\toprule
 &   \multicolumn{ 2 }{c}{ telework }\\ 
  & 0 & 1 \\ 
 & n = 79 & n = 216 \\ 
 \midrule
gender &   &  \\ 
\hspace{6pt}    0 & 52 (65.8\%) & 101 (46.8\%)\\ 
\hspace{6pt}    1 & 27 (34.2\%) & 115 (53.2\%)\\ 
age &   &  \\ 
\hspace{6pt}   & 46.7 (8.0) & 45.2 (8.5)\\ 
r\_years &   &  \\ 
\hspace{6pt}   & 17.6 (12.5) & 18.5 (9.4)\\ 
race &   &  \\ 
\hspace{6pt}    Asian or Asian American & 6 (7.6\%) & 25 (11.6\%)\\ 
\hspace{6pt}    Black or African American & 7 (8.9\%) & 12 (5.6\%)\\ 
\hspace{6pt}    Latinx or Hispanic & 4 (5.1\%) & 14 (6.5\%)\\ 
\hspace{6pt}    Middle Eastern & 0 (0\%) & 2 (0.9\%)\\ 
\hspace{6pt}    Other & 0 (0\%) & 1 (0.5\%)\\ 
\hspace{6pt}    Prefer not to answer & 0 (0\%) & 2 (0.9\%)\\ 
\hspace{6pt}    White or European American & 61 (77.2\%) & 159 (73.6\%)\\ 
\hspace{6pt}    White or European American,Latinx or Hispanic & 1 (1.3\%) & 1 (0.5\%)\\ 
childnum &   &  \\ 
\hspace{6pt}   & 0.7 (0.9) & 0.9 (1.5)\\ 
income &   &  \\ 
\hspace{6pt}   & 62,494.7 (66,422.0) & 81,768.9 (116,748.9)\\ 
\bottomrule

\end{tabular}
\end{table}


```{r, results = 'asis'}
#df2latex(summary_tbl)
```