---
title: "Untitled"
author: "Iris Zhong"
date: "3/31/2021"
output: html_document
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(readr)
library(lubridate)
library(here)
```

```{r import data}
# import premeasures
prem <- read.csv(here("TeleCom_Dyad_premeasures.csv"))
# import daily diary
diary <- read.csv(here("TeleCom_Dyad_dailydiary.csv"))
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, include = F}
#diary <- diary %>%
#  mutate(partID = case_when(partID_given == "" ~ partID,
#                            partID_given != "" ~ partID_given))
#diary <- diary %>%
#  mutate(partID = str_replace_all(partID, " ", ""),
#         partID = str_replace_all(partID, ":", ""),
#         partID = str_replace(partID, "R-", "R_"),
#         partID = str_remove(partID,"\\."),
#         partID = ifelse(str_starts(partID,"R", negate = T ),
#                         paste0("R_",partID), partID))
         
```



```{r}
temp <- diary %>%
  mutate(RecordedDate = mdy_hm(RecordedDate)) %>%
  arrange(dyadID, partID, day, RecordedDate) %>%
  mutate(ResponseID = seq_along(RecordedDate)) %>%
  group_by(partID, day) %>%
  mutate(RecordedDate_lag = lag(RecordedDate), #so we can test if record for second tuesday are plausibly next week
         dist = difftime(RecordedDate, RecordedDate_lag, units = "days"), #recoding as day between
         first_sec = seq_along(RecordedDate), #first tuesday or second tuesday?
         prob = ifelse(first_sec >= 2 & dist < 4, 1, 0)) %>% #second+ tuesday is problematic if it's NOT plausibly next week
  group_by(dyadID, partID) %>%
  arrange(dyadID, partID, RecordedDate) %>%
  mutate(rec_num = seq_along(RecordedDate),
         weekish = ifelse(rec_num > 7, 2, 1), #coding for days beyond 7, most are "week 2"
         day_of_study = ifelse(weekish == 2 | (weekish==1 & first_sec>1), #for people who missed days in week 1
                        (case_when(day == "Monday" ~ 8,
                        day == "Tuesday" ~ 9,
                        day == "Wednesday" ~ 10,
                        day == "Thursday" ~ 11,
                        day == "Friday" ~ 12,
                        day == "Saturday" ~ 13,
                        day == "Sunday" ~ 14)), 
                      case_when(day == "Monday" ~ 1,
                        day == "Tuesday" ~ 2,
                        day == "Wednesday" ~ 3,
                        day == "Thursday" ~ 4,
                        day == "Friday" ~ 5,
                        day == "Saturday" ~ 6,
                        day == "Sunday" ~ 7)),
         week = ifelse(day_of_study > 7, 2, 1)) %>%
  group_by(partID) %>%
  mutate(problems = sum(prob)) %>%
  arrange(desc(problems), dyadID, partID, RecordedDate) #%>%
  #select(ResponseID, partID, partID_given, problems, dyadID, RecordedDate, day, day_of_study)
```


```{r}
temp <- temp %>%
  mutate(partID_given = str_replace_all(partID_given, " ", ""),
         partID_given = str_replace_all(partID_given, "\\:", ""),
         partID_given = str_replace(partID_given, "R-", "R_"),
         partID_given = str_remove(partID_given,"\\."),
         partID_given = ifelse(str_starts(partID_given,"R", negate = T ) & partID_given != "",
                         paste0("R_",partID_given), partID_given))
         
         
# Create an indicator of partID_given and partID match
temp <- temp %>%
  mutate(ID_check = case_when(partID_given == "" ~ 0,
                              partID_given == partID ~ 1,
                              partID_given != partID ~ 2)) %>%
  mutate(partID = ifelse(ID_check == 1, partID_given, partID))
         
  


```

```{r}
temp <- temp %>%
  filter(problems <= 1 & ID_check != 2) 
 # if partID_given is empty / partID_given == partID
```

```{r}
temp_small <- temp %>%
  filter(partID != "R_1fiPEJydpvuaEEs" & partID != "R_1jV9NyWEbelB76s" & partID != "R_1PTxhk4207mTHAb" & partID != "R_27kuznipTrWICLB" & partID != "R_ODPL8q3q4Shtvr3"  ) %>%
  filter(ResponseID != 145 & ResponseID != 1266 &ResponseID != 1278 & ResponseID != 1282&ResponseID != 1302 & ResponseID != 2800)
```

```{r}
temp_small <- temp_small %>%
  mutate(day = ifelse(ResponseID == 494, "Friday", day),
         day = ifelse(ResponseID == 771, "Wednesday", day),
         day = ifelse(ResponseID == 873, "Monday", day),
         day = ifelse(ResponseID == 887, "Monday", day),
         day = ifelse(ResponseID == 1077, "Wednesday", day),
         day = ifelse(ResponseID == 1111, "Saturday", day),
         day = ifelse(ResponseID == 1202, "Wednesday", day),
         day = ifelse(ResponseID == 1219, "Tuesday", day),
         day = ifelse(ResponseID == 1233, "Tuesday", day),
         day = ifelse(ResponseID == 1247, "Tuesday", day),
         day = ifelse(ResponseID == 1282, "Monday", day),
         day = ifelse(ResponseID == 1365, "Saturday", day),
         day = ifelse(ResponseID == 1771, "Friday", day),
         day = ifelse(ResponseID == 1785, "Friday", day),
         day = ifelse(ResponseID == 2328, "Wednesday", day),
         day = ifelse(ResponseID == 2345, "Saturday", day),
         day = ifelse(ResponseID == 2393, "Wednesday", day),
         day = ifelse(ResponseID == 2516, "Thursday", day),
         day = ifelse(ResponseID == 2680, "Monday", day),
         day = ifelse(ResponseID == 2694, "Monday", day),
         day = ifelse(ResponseID == 2804, "Monday", day),
         day = ifelse(ResponseID == 2821, "Saturday", day),
         day = ifelse(ResponseID == 2825, "Sunday", day),
         day = ifelse(ResponseID == 2859, "Wednesday", day),
         day = ifelse(ResponseID == 2881, "Sunday", day),
         day = ifelse(ResponseID == 2940, "Thursday", day),
         day = ifelse(ResponseID == 3005, "Monday", day),
         day = ifelse(ResponseID == 3025, "Thursday", day),
         day = ifelse(ResponseID == 3178, "Monday", day),
          day = ifelse(ResponseID == 3192, "Monday", day),
         day = ifelse(ResponseID == 3243, "Sunday", day),
         day = ifelse(ResponseID == 3385, "Wednesday", day),
         day = ifelse(ResponseID == 3399, "Wednesday", day),
         # error spotted from obsid
         day_of_study = ifelse(ResponseID == 904, 8, day_of_study),
         day = ifelse(ResponseID == 1157, "Monday", day)
         )
```

Randi's cleaning:

remove anyone with 
(problems > 1) | (problems == 1 & !is.na(partID_given)) 

other problematic cases or IDs to filter out completely: 
145, 1266, 1278, 1282, 1302, partID == R_1fiPEJydpvuaEEs, R_1jV9NyWEbelB76s,R_1PTxhk4207mTHAb, R_27kuznipTrWICLB, R_ODPL8q3q4Shtvr3, 2800

other problematic cases to fix due to participant error: 
494 says thrusday but change to Friday
771 says thursday but change to Wednesday
873 says Tuesday but change to Monday
887 say Tues but change to Mon
894 is day 8 but it gets coded as day 1
1077 says Thurs but it's Wed
1111 says Fri but it's sat
1202 says Thurs but it's Wed
1219 says Wed but it's Tues
1233 says Wed but it's Tues
1247 says Wed but it's Tues
1282 says Sun but Mon
1365 says Fri but it's sat
1771 says sat but it's fri
1785 says sat but it's fri
2328 says Tues but it's Wed
2345 says fri but it's sat
2393 says thur but it's wed 
2516 says wed but it's thurs
2680 say Tues but it's mon
2694 says tues but it's mon
2804 says Sun but mon
2821 says fri but it's sat
2825 says sat but it's sun
2859 says tues but it's wed
2881 say sat but it's sun
2940 says fri but it's thur
3005 says tue but it mon
3025 says fri but its thur
3178 says Tue but its mon 
3192 says tues but it's mon 
3243 says sat but it's sun 
3385 says tues but it's wed
3399 says tues but it's wed

```{r}
#run again after clean:
temp_small_2 <- temp_small %>%
  arrange(dyadID, partID, day, RecordedDate) %>%
  mutate(ResponseID = seq_along(RecordedDate)) %>%
  group_by(partID, day) %>%
  mutate(RecordedDate_lag = lag(RecordedDate), #so we can test if record for second tuesday are plausibly next week
         dist = difftime(RecordedDate, RecordedDate_lag, units = "days"), #recoding as day between
         first_sec = seq_along(RecordedDate), #first tuesday or second tuesday?
         prob = ifelse(first_sec >= 2 & dist < 4, 1, 0)) %>% #second+ tuesday is problematic if it's NOT plausibly next week
  group_by(dyadID, partID) %>%
  arrange(dyadID, partID, RecordedDate) %>%
  mutate(rec_num = seq_along(RecordedDate),
         weekish = ifelse(rec_num > 7, 2, 1), 
         day_of_study = ifelse(weekish == 2 | (weekish==1 & first_sec>1), 
                        (case_when(day == "Monday" ~ 8,
                        day == "Tuesday" ~ 9,
                        day == "Wednesday" ~ 10,
                        day == "Thursday" ~ 11,
                        day == "Friday" ~ 12,
                        day == "Saturday" ~ 13,
                        day == "Sunday" ~ 14)), 
                      case_when(day == "Monday" ~ 1,
                        day == "Tuesday" ~ 2,
                        day == "Wednesday" ~ 3,
                        day == "Thursday" ~ 4,
                        day == "Friday" ~ 5,
                        day == "Saturday" ~ 6,
                        day == "Sunday" ~ 7)),
         week = ifelse(day_of_study > 7, 2, 1))# %>%
  #dplyr::select(ResponseID, dyadID, partID, RecordedDate, day, day_of_study)
```

Another round of cleaning
737834： 3 --> 8
7403083 remove because of recorded date
17986423 remove because of recorded date
R_D82yWXQCPehTYOd: 14 --> 7
R_r86LixcW9gMWsaB: 14 --> 7
19323251 remove because of recorded date
R_PRsfimNYXTe5Jpn, responseID == 1: remove because of NA response
R_2SIj7HaPcdaT1YB: 1 --> 8, remove day_of_study == 13 (because unrecognized date)
R_3J3nDgtBTAsgvAR: 1 --> 8, remove day_of_study == 13/14
R_3J3nDgtBTAsgvAR: ResponseID == 6 --> day = Monday, day_of_study=1
		   ResponseID == 7 --> day_of_study = 7
Remove R_3JCcOgGFZfWXkVD: responseID == 3 (extra day)
Remove 29169727 because of recorded date
Remove 29187228 day_of_study == 10 (redundant)
Remove 29358468 because of recorded date
R_VPdzuocBY7uAHTj: day_of_study 1 --> 8
Remove 29469928 because of recorded date
Remove 29472035 because of recorded date
Remove R_1q3UDwRbwY02PZ3, response ID ==1: NA response
Remove 29532872, responseID == 5 (extra day)
Remove 29536578 because of recorded date
Remove 29559028 because of recorded date
Remove 29577345 because of recorded date
Remove R_ODPL8q3q4Shtvr3 because of messy data
R_31MkJYIh2I3XWnP: day_of_study 2-->9
Remove 29733249 because of recorded date
R_XHsG67d7Lv5N09r: day Tuesday --> Thursday, day_of_study 9 --> 4
Remove 29758869 because of recorded date
Remove  29759818 because of recorded date
dyad ID == 31256405: remove ResponseID == 9 (redundant)
Remove R_2TBRBwuCwt5nHIB, responseID == 1 (NA response)
Remove 31635308 because of recorded date
Remove R_3NwwT3kjHCJHcge, responseID == 14 (redundant)
remove 32166157 because of recorded date
remove 32997534 because of recorded date
remove 33703455 because of recorded date
remove 1836239 because of recorded date
R_3J3nDgtBTAsgvAR: remove responseID == 6; responseID == 7 --> day_of_study = 14
R_TuUDpU6tnQ77WPT: remove responseID == 4/5

```{r}
# Day/day of study errors
temp_small_2 <- temp_small_2 %>%
  mutate(day_of_study = ifelse(dyadID == 737834 & day_of_study == 1, 8,day_of_study),
         day_of_study = ifelse(partID == "R_D82yWXQCPehTYOd" & day_of_study == 14, 7, day_of_study),
         day_of_study = ifelse(partID == "R_r86LixcW9gMWsaB" & day_of_study == 14, 7, day_of_study),
        # day_of_study = ifelse(dyadID == 27005905 & day_of_study == 1, 8,day_of_study),
         day_of_study = ifelse(partID == "R_3J3nDgtBTAsgvAR" & ResponseID == 6, 1, day_of_study),
         day = ifelse(partID == "R_3J3nDgtBTAsgvAR" & ResponseID == 6, "Monday", day),
         day_of_study = ifelse(partID == "R_3J3nDgtBTAsgvAR" & ResponseID == 7, 7, day_of_study),
         day_of_study = ifelse(partID == "R_3J3nDgtBTAsgvAR" & day_of_study == 1, 8, day_of_study),
         day_of_study = ifelse(partID == "R_31MkJYIh2I3XWnP" & day_of_study == 2, 9, day_of_study),
         day_of_study = ifelse(partID == "R_XHsG67d7Lv5N09r" & day_of_study == 9, 4, day_of_study),
         day = ifelse(partID == "R_XHsG67d7Lv5N09r" & day_of_study == 4, "Thursday", day),
        day_of_study = ifelse(partID == "R_3J3nDgtBTAsgvAR" & ResponseID == 7, 14, day_of_study))
         
         
```

```{r}
temp_small_2$ResponseID_chr <- as.character(temp_small_2$ResponseID)
```


```{r}
# Remove redundant/NA responses

temp_small_2 <- temp_small_2 %>%
  filter(partID != "R_PRsfimNYXTe5Jpn" | ResponseID != 1) %>%
  filter(partID != "R_2SIj7HaPcdaT1YB" | day_of_study != 13) %>%
  #filter(partID != "R_3J3nDgtBTAsgvAR" | day_of_study != 13) %>%
  #filter(partID != "R_3J3nDgtBTAsgvAR" | day_of_study != 14) %>%
  filter(partID != "R_3JCcOgGFZfWXkVD" | ResponseID != 3) %>%
  filter(dyadID != 29187228 | day_of_study != 10) %>%
  filter(dyadID != 29532872 | ResponseID != 5) %>%
  filter(dyadID != 31256405 | ResponseID != 9) %>%
  filter(partID != "R_2TBRBwuCwt5nHIB" | ResponseID != 1) %>%
  filter(partID != "R_3NwwT3kjHCJHcge" | ResponseID != 14) %>%
  filter(partID != "R_3J3nDgtBTAsgvAR" | ResponseID != 6) %>%
  filter(partID != "R_TuUDpU6tnQ77WPT" | ResponseID != 4) %>%
  filter(partID != "R_TuUDpU6tnQ77WPT" | ResponseID != 5)
#temp_small_2 <- temp_small_2 %>%


```
R_3J3nDgtBTAsgvAR

```{r}
# Remove dyads filling out surveys in different weeks

temp_small_2 <- temp_small_2 %>%
  filter(dyadID != 7403083 & dyadID != 17986423 &dyadID != 19323251 & dyadID != 29169727 &dyadID != 29358468 & dyadID != 29469928 &dyadID != 29472035 & dyadID != 29536578 & dyadID != 29559028 & dyadID != 29577345 & dyadID != 29733249 &dyadID != 29758869 & dyadID != 29759818 & dyadID != 31635308 &dyadID != 32166157 & dyadID != 32997534 & dyadID != 33703455 & dyadID != 1836239)
```

```{r}
temp_small_2 <- temp_small_2 %>%
  mutate(obsid = day_of_study+14*(dyadID-1))

```


```{r}
write.csv(temp_small_2,"final_diary_data.csv", row.names = FALSE)
```





