---
title: "Scales"
author: "Yena Li"
date: "3/28/2021"
output: html_document
---

These are instructions for computing **scale scores** of constructs, e.g., marital quality: love, to be used in subsequent analyses. If you want to use the marital quality scale (which consists of **items**, w11mar1_A - w11mar25_A) you will first need to create scale scores for the 4 sub-scales: Love, Maintenance, Conflict, and Ambivalence.


```{r, message=FALSE}
library(dplyr)
library(psych)
library(here)
library(ggplot2)
library(nlme)
```

#Step 1: Look at the correlation matrix for each sub-scale

```{r}
View(prem)
View(diary)
```

## Qmi

### 1.Re-code for "Not true about me" = 1, "A little true about me" = 2, "Somewhat true about me" = 3, "Mostly true about me" = 4

```{r}
diary <- diary %>%
  mutate(qmi1.r = recode(qmi1, "Not true about me" = 1, "A little true about me" = 2, "Somewhat true about me" = 3, "Mostly true about me" = 4))
```

```{r}
diary <- diary %>%
  mutate(qmi2.r = recode(qmi2, "Not true about me" = 1, "A little true about me" = 2, "Somewhat true about me" = 3, "Mostly true about me" = 4))
```

```{r}
diary <- diary %>%
  mutate(qmi3.r = recode(qmi3, "Not true about me" = 1, "A little true about me" = 2, "Somewhat true about me" = 3, "Mostly true about me" = 4))
```

```{r}
diary <- diary %>%
  mutate(qmi4.r = recode(qmi4, "Not true about me" = 1, "A little true about me" = 2, "Somewhat true about me" = 3, "Mostly true about me" = 4))
```

### 2.Corr.Matrix

```{r}
#qmi1`
corr.test(select(diary, qmi1.r, qmi2.r, qmi3.r, qmi4.r))$r
```

## Gender role belief scale

### 1.Re-code for "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5

```{r}
prem <- prem %>%
  mutate(grbs_1.r = recode(grbs_1,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_2.r = recode(grbs_2,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_3.r = recode(grbs_3,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_4.r = recode(grbs_4,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_5.r = recode(grbs_5,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_6.r = recode(grbs_6,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_7.r = recode(grbs_7,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_8.r = recode(grbs_8,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_9.r = recode(grbs_9,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_10.r = recode(grbs_10,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_11.r = recode(grbs_11,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_12.r = recode(grbs_12,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_13.r = recode(grbs_13,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_14.r = recode(grbs_14,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_15.r = recode(grbs_15,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_16.r = recode(grbs_16,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_17.r = recode(grbs_17,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_18.r = recode(grbs_18,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_19.r = recode(grbs_19,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

```{r}
prem <- prem %>%
  mutate(grbs_20.r = recode(grbs_20,  "Strongly disagree" = 1, "Somewhat disagree" = 2, "Neither agree nor disagree" = 3, "Somewhat agree" = 4, "Strongly agree" = 5))
```

### 2.Corr.Matrix

```{r}
#grbs`
corr.test(select(prem, grbs_1.r, grbs_2.r, grbs_3.r, grbs_4.r, grbs_5.r, grbs_6.r, grbs_7.r, grbs_8.r, grbs_9.r, grbs_10.r, grbs_11.r, grbs_12.r, grbs_13.r, grbs_14.r, grbs_15.r, grbs_16.r, grbs_17.r, grbs_18.r, grbs_19.r, grbs_20.r))$r
```

#Step 2: Reverse scaore any items that need it

Based on the correlation matrices you computed above, decide if you need to reverse code any variables. In this case, we do not. But in many other situations you will need to. As an example, you can use the following code to reverse the second item. Note the `.r` added to the new variable. 

Needs to be revised: 2,3,7,10,12,17

```{r}
prem <- prem %>%
  mutate(grbs_2.r = (1 + 5) - grbs_2.r)
```

```{r}
prem <- prem %>%
  mutate(grbs_3.r = (1 + 5) - grbs_3.r)
```

```{r}
prem <- prem %>%
  mutate(grbs_7.r = (1 + 5) - grbs_7.r)
```

```{r}
prem <- prem %>%
  mutate(grbs_10.r = (1 + 5) - grbs_10.r)
```

```{r}
prem <- prem %>%
  mutate(grbs_12.r = (1 + 5) - grbs_12.r)
```

```{r}
prem <- prem %>%
  mutate(grbs_17.r = (1 + 5) - grbs_17.r)
```

#Step 3: Look at correlation matrix again, this time using reversed items

```{r, eval = FALSE}
corr.test(select(prem, grbs_1.r, grbs_2.r, grbs_3.r, grbs_4.r, grbs_5.r, grbs_6.r, grbs_7.r, grbs_8.r, grbs_9.r, grbs_10.r, grbs_11.r, grbs_12.r, grbs_13.r, grbs_14.r, grbs_15.r, grbs_16.r, grbs_17.r, grbs_18.r, grbs_19.r, grbs_20.r))$r
```

#Step 4: Once all of teh correaltions are positive, calculate the reliability, using revsered items. 

You want to look at `raw_alpha` in the output!

```{r}
psych::alpha(select(diary, qmi1.r, qmi2.r, qmi3.r, qmi4.r))
```

```{r}
psych::alpha(select(prem, grbs_1.r, grbs_2.r, grbs_3.r, grbs_4.r, grbs_5.r, grbs_6.r, grbs_7.r, grbs_8.r, grbs_9.r, grbs_10.r, grbs_11.r, grbs_12.r, grbs_13.r, grbs_14.r, grbs_15.r, grbs_16.r, grbs_17.r, grbs_18.r, grbs_19.r, grbs_20.r))
```

Ideally the reliabilities would be above .70. In this case, the reliabilities for conflict and maintenance are less than .70. There's not much as can do about this, besides dropping an item or two. Note that if you drop mar15 from the conflict scale, the reliability would go up to .68. This is your call. 

#Step 5: If alpha is >=.70, calculate the scale scores.  

```{r}
#qmi
diary$qmi_ss <- rowMeans(select(diary, qmi1.r, qmi2.r, qmi3.r, qmi4.r), na.rm = TRUE)
```

```{r}
#grbs
prem$grbs_ss <- rowMeans(select(prem, grbs_1.r, grbs_2.r, grbs_3.r, grbs_4.r, grbs_5.r, grbs_6.r, grbs_7.r, grbs_8.r, grbs_9.r, grbs_10.r, grbs_11.r, grbs_12.r, grbs_13.r, grbs_14.r, grbs_15.r, grbs_16.r, grbs_17.r, grbs_18.r, grbs_19.r, grbs_20.r), na.rm = TRUE)
```

# ICC

```{r}
qmi_mod <- gls(qmi_ss ~ 1, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID), 
                 data=diary)
```

```{r}
grbs_mod <- gls(grbs_ss ~ 1, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID), 
                 data=prem)
```

We use gls as it allows us to correlate the errors of the two members.

gls Statement Explained  

`empty_mod =`                             object name where the results are located   
`gls()`                                    statistical procedure used  
`tension_A ~`                              outcome variable name in the dataset    
`genderE_A,`                   predictors variables in the dataset 
`na.action=na.omit,`                       needed if there are missing data  
`correlation=corCompSymm (form=~1|cuplid),`  correlates errors of the two members from the same dyad, Dyad is the ID variable for dyad      
`data=acitelli_pair`                              name of the dataset in R (see above)      


##Output

```{r}
summary(qmi_mod)
```
```{r}
summary(grbs_mod)
```

To look at the measure of nonindependence, which can be accessed by:

```{r}
coef(empty_mod$model$corStruct, unconstrained = FALSE)
```

This is partial intraclass correlation.  That is, it the correlations between the two members' perceptions of tension, controlling for both gender.   

```

